Identifying Values to Express Emotions with a Non-Anthropomorphic Platform

### 2016-10-08 JournalIJSR/Parts/ExperimentDesign.tex
Changes in both articles.
Add files via upload

The experiment was designed to get a better understanding about the contribution linear and angular velocity, oscillation angle, direction, and orientation to express happiness, anger, sadness and fear, which are four out of six emotions considered by Ekman~\cite{Ekman2004} as basic emotions.
%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%

@@

\begin{itemize}
	\item \textbf{Angular velocity} is the rotational speed  ($\omega$) of the robot with respect to its center.

	\item \textbf{Oscillation angle} is the maximum extension in which the robot will rotate around its center in the oscillating movement ($\theta$).

@@

	\item \textbf{Direction with respect to participant's perspective} is the angle generated from the participant's point of view with respect to the robots trajectory ($D$).

@@

The three first variables are shown in Figure~\ref{fig:angular_movement}. As it could be observed, robot's frame of reference is draw to show that it could move straight while is rotating.

\begin{figure}
	\centering
	\includegraphics[width=0.80\textwidth]{./Images/ExampleMovement.png} 
	\caption{Example of the features used in the experiment. $x$ represents the displacement in meters, $\omega$ is the angular velocity ($rad/s$) and $\theta$ the oscillation of the body around its center ($rad$). The upper sequence depicts a movement based only on linear velocity, while the bottom one shows a sequence with angular and linear movement. The two black arrows in the robot's middle depict robot's frame of reference.}
	\label{fig:angular_movement}

@@

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\subsection{Dependent Variables}

\begin{itemize}
	\item \textbf{Emotion:} is the feeling perceived by the participants from the robot's movement. From previous experiences %TODO cite
	, it was decided to ask the participants to select an emotion name in a list including the four emotions intended to be expressed,  two mental states that could be misinterpreted from these emotions, and the option of ``other'', where participants could write their own interpretation. 
	The two  states of mind included as confounding terms are tenderness and excitement, which correspond to low and high arousal states.

	\item \textbf{Emotion's intensity:} indicate the emotion intensity as perceived by the subject. This variable is measured on a ten point scale rate, ranging from 0 to 10, where 0 means that the corresponding emotion is not perceived by the subject and 10 that the emotion is highly perceived by the subject.

\end{itemize}
%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\subsection{Independents' Variables Values}

It was decided to select specific for all independents variables, discrete values to make the experiment feasible. First, a simple test to evaluate when significant changes could be perceived was performed on a small sample of independent subjects. Base on this test specific values for oscillation angle, and angular and linear velocities were selected. For the remaining two variables were selected the cases that could be beneficial for the experiment. 
The chosen values are shown in Table~\ref{table:variables_values}.

\begin{table}[htb]
\caption{Possible values for each of the independent variables.}
\begin{tabular}{|c|c|c|c|c|}
\hline
\backslashbox{Variable}{Possibilities} & First & Second & Third & Fourth\\
\hline   
Angular Velocity ($rad/sec$)& $0$ & $1$ & $2$ & $3$\\
\hline
Oscillation Angle ($rad$)& $0$ & $0.087$ & $0.175$ & $0.349$\\
\hline
Linear Velocity ($mm/sec$) & $0$ & $200$ & $500$ & $900$\\
\hline
Direction ($rad$)&$0$&$\pi$&$\frac{-\pi}{2}$& \\
\hline
Orientation ($rad$) & $0$ & $\pi$ & & \\
\hline 
\multicolumn{5}{c}{}
\end{tabular} 
\label{table:variables_values}
\end{table}

@@

\begin{figure}
	\centering
	\includegraphics[width=1.0\textwidth]{./Images/possibilities_case.png} 
	\caption{Combination of direction and orientation. The crosses symbolize the final position. The robot represents the initial position with its orientation, which is represented through the robot's frame of reference. The dash big square represents robot's movement zone, while the small represents participant's zone. a) Direction = $0$ and Orientation = $0$. b) Direction = $0$ and Orientation = $\pi$. c) Direction = $\pi$ and Orientation = $\pi$. d) Direction = $\pi$ and Orientation = $0$. e) Direction = $\frac{-\pi}{2}$ and Orientation = $0$. f) Direction = $\frac{-\pi}{2}$ and Orientation = $\pi$}
	\label{fig:possibilities_orientation_direction}
\end{figure}

The experiences, meant as desired procedures to compare~\cite{oehlert2000first}, were generated from the combination of independent variables' values for a total of 384 combinations. All the experiences that would not add any significant information to the experiment were deleted, such as experiences with $\theta=0$ and $\omega \neq 0$, which reduced the total amount of treatments to 195.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\subsection{Participants' Sequence}

It was decided that each subject will be just exposed to twenty over one hundred and ninety five possible experiences, which lasted  from 10 to 15 minutes. This was decided because each subject was a volunteer and would not perceive any monetary remuneration, so the time dedicated to the experiment had to be kept limited. The twenty treatments were selected picking a number without replacement from 1 to 195.
%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%

@@

The experiment's setup and dimensions are shown in the Figure~\ref{fig:setup}. The crosses symbolize possible starting points, which were selected depending on the direction's value, as it is showed in Figure~\ref{fig:possibilities_orientation_direction}.

\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{./Images/ExperimentGeneral.png} 
	\caption{Setup for the experiment. The crosses symbolize the possible starting points.}
	\label{fig:setup}
\end{figure}

>>>>

The experiment was designed to get a better understanding about the contribution linear and angular velocity, oscillation angle, direction, and orientation can give to the expression of happiness, anger, sadness, and fear, which are four out of the six emotions considered by Ekman~\cite{Ekman2004} as basic emotions.
%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%

@@

\begin{itemize}
	\item \textbf{Angular velocity} is the rotational velocity  ($\omega$) of the robot with respect to its center.

	\item \textbf{Oscillation angle} is the maximum extension of the robot's rotation around its center in the oscillating movement ($\theta$).

@@

	\item \textbf{Direction with respect to participant's perspective} is the angle generated from the participant's point of view with respect to the robot's trajectory ($D$).

@@

The three first variables are shown in Figure~\ref{fig:angular_movement}. The robot's frame of reference is drawn to show that it could move straight while it is rotating.

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{./Images/ExampleMovement.png} 
	\caption{Example of the features used in the experiment. $x$ represents the displacement in meters, $\omega$ is the angular velocity ($rad/s$) and $\theta$ the oscillation of the body around its center ($rad$). The upper sequence depicts a movement based only on linear velocity, while the bottom one shows a sequence with angular and linear movement. The two black arrows in the robot's middle depict robot's frame of reference.}
	\label{fig:angular_movement}

@@

\subsubsection*{Independent Variables values}

Specific, discrete values were selected for all independent variables, to make the experiment feasible. First, a simple test to evaluate when significant changes could be perceived was performed on a small sample of independent subjects. Based on this test, specific values for oscillation angle, and angular and linear velocities were selected. The values for the remaining two variables were selected according to what was needed by the experiment. %TODO I've tried to make this sentence clearer, but it is still obscure. What does it mean?

The chosen values are shown in Table~\ref{table:variables_values}.

\begin{table}[htb]
\centering
\caption{Values for each of the independent variables in the experiment.}
\begin{tabular}{|c|c|c|c|c|}
\hline
\backslashbox{Variable}{Possibilities} & First & Second & Third & Fourth\\
\hline   
Angular Velocity ($rad/sec$)& $0$ & $1$ & $2$ & $3$\\
\hline
Oscillation Angle ($rad$)& $0$ & $0.087$ & $0.175$ & $0.349$\\
\hline
Linear Velocity ($mm/sec$) & $0$ & $200$ & $500$ & $900$\\
\hline
Direction ($rad$)&$0$&$\pi$&$\frac{-\pi}{2}$& \\
\hline
Orientation ($rad$) & $0$ & $\pi$ & & \\
\hline 
\multicolumn{5}{c}{}
\end{tabular} 
\label{table:variables_values}
\end{table}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{./Images/possibilities_case.png} 
	\caption{Combination of direction and orientation. The crosses symbolize the final position. The robot represents the initial position with its orientation, which is represented through the robot's frame of reference. The dashed big square represents the robot's movement zone, while the small one on the side represents the subjects' zone. a) Direction = $0$ and Orientation = $0$. b) Direction = $0$ and Orientation = $\pi$. c) Direction = $\pi$ and Orientation = $\pi$. d) Direction = $\pi$ and Orientation = $0$. e) Direction = $\frac{-\pi}{2}$ and Orientation = $0$. f) Direction = $\frac{-\pi}{2}$ and Orientation = $\pi$}
	\label{fig:possibilities_orientation_direction}
\end{figure}

The experiences, meant as desired procedures to compare~\cite{oehlert2000first}, %TODO What does "desired procedures to compare" mean?
were generated from the combination of independent variables' values for a total of 384 combinations. All the experiences that would not add any significant information to the experiment were removed, such as experiences with $\theta=0$ and $\omega \neq 0$, which reduced the total amount of experiences to 195.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\subsection{Dependent Variables}

\begin{itemize}
	\item \textbf{Emotion} is the feeling perceived by the participants from the robot's movement. From previous experiences %TODO cite
	, it was decided to ask the participants to select an emotion name in a list including the four emotions intended to be expressed, two mental states that could be misinterpreted from these emotions, and the option of ``other''. 
	The two  states of mind included as confounding terms are tenderness and excitement, which correspond to low and high arousal states.

	\item \textbf{Emotion's intensity} indicates the emotion intensity as perceived by the subject. This variable is measured on a ten point scale rate, ranging from 0 to 10, where 0 means that the corresponding emotion is not perceived by the subject and 10 that the emotion is highly perceived by the subject.

\end{itemize}
%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%
\subsection{Participants}

It was decided that each subject had to be exposed to twenty over one hundred and ninety five possible experiences, trial that lasted  from 10 to 15 minutes. This was decided because each subject was a volunteer, so the time dedicated to the experiment had to be kept limited. The twenty treatments were selected picking a number without replacement from 1 to 195. A total of 980 answers were collected, guaranteeing a minimum of 5 trials for each motion type.

The experiment was performed at Politecnico di Milano, involving subjects with different backgrounds.
A total of 49 volunteers were involved: 12 females and 37 males. The average age of the subjects was 25.28, with standard deviation of 2.8, with a minimum age of 20 and maximum of 32. The subjects' country of origin and their backgrounds are shown in the Table~\ref{table:country} and Table~\ref{table:career}, respectively.

%%%%%%%%%%%%%%%%%%%%% 
\begin{table}[h]
\centering
\caption{Subjects' Country of origin.}
\label{table:country}
\begin{tabular}{|c|c|}
\hline
\textbf{Country} & \textbf{Counting} \\
\hline
Albania & 1 \\
\hline
Bosnia & 1 \\
\hline
Brazil & 2 \\
\hline
Colombia & 4 \\
\hline
Germany & 1 \\
\hline
Greece & 1 \\
\hline
Iran & 5 \\
\hline
Italy & 33 \\
\hline
Moldova & 1 \\
\hline 
\multicolumn{2}{c}{}
\end{tabular} 
\end{table}
%%%%%%%%%%%%%%%%

\begin{table}[h]
\centering
\caption{Subjects' Background.}
\label{table:career}
\begin{tabular}{|c|c|}
\hline
\textbf{Career} & \textbf{Counting}\\
\hline
Aeronautical Engineering & 1 \\
\hline
Architecture & 1 \\
\hline
Social assistance & 1 \\
\hline
Automation & 1 \\
\hline
Bio-medical Engineering & 5 \\
\hline
Computer Science & 33 \\
\hline
Electronic Engineering & 2 \\
\hline
Mechanical Engineering & 2 \\
\hline
Nursery & 1 \\
\hline
Pedagogical Science & 1 \\
\hline
Tourism & 1 \\
\hline
\multicolumn{2}{c}{}
\end{tabular} 
\end{table}
 %TODO I would say how many times each experience was tested. This is a needed parameter for this experimental setup.
%%%%%%%%%%%%%%%%%%%

The information from each subject was collected using a web-based form. To maintain anonymity, no personal information that could be used to trace the subject back was collected. The procedure used with each subject is described here below.

\begin{enumerate}

	\item The subject was asked to fill out the following information:

	\begin{itemize}
		\item Sex
		\item Background
		\item Age
		\item Country of origin
	\end{itemize}

	\item The robot was shown to the participant and the experiment procedure explained.

	\item An example of the questionnaire was presented and a sample movement of the robot shown.

	\item The subject was exposed to a specific movement sequence according to the following steps:

	\begin{enumerate}

		\item The subject is exposed to the movement generated by a configuration of values.

		\item The subject could use as much time as needed to select values for intensity of the different terms in the questionnaire.

		\item After the subject had completed his/her selection about the current movement, the robot is positioned to the new starting point, and the sequence is repeated from step 1.(a) for the rest of movements.

	\end{enumerate}
\end{enumerate}

The order of the options enlisted in the questionnaire changed for each question to prevent any kind of bias. Figure~\ref{fig:questionnaire_example} shows an example of the questionnaire used.

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{./Images/example_survey.png} 
	\caption{Example of the questionnaire used in the experiment.}
	\label{fig:questionnaire_example}
\end{figure}

@@

The experimental setup and dimensions are shown in the Figure~\ref{fig:setup}. The crosses symbolize possible starting points, which were selected depending on the direction's value, as it is showed in Figure~\ref{fig:possibilities_orientation_direction}.

\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{./Images/ExperimentGeneral.png} 
	\caption{Setup for the experiment. The crosses symbolize the possible starting points.}
	\label{fig:setup}
\end{figure}

### 2016-10-08 JournalIJSR/Parts/Introduction.tex
Add files via upload

Emotions and mental states are not just expressed through facial expression but also by body through postures and other features~\cite{Gelder2008}. However  many psychological studies have been mostly focused on understanding the role of human face in emotion projection~\cite{Ekman2004},~\cite{kleinsmith2012affective} and mental states. This trend has been followed by the robotics community, where anthropomorphic faces (e.g.,~\cite{Arras2012},~\cite{Breazeal2002}) and bodies (e.g.,~\cite{Canamero2010},~\cite{haering2011},~\cite{Destephe2013}) have been used to convey emotions.
Nevertheless in many situations the presence of anthropomorphic elements would be out of place and not justified by the main robot's functionalities. Most of the current and future robotics platforms on the market will not require anthropomorphic faces~\cite{Breazeal2002} or limbs~\cite{Li2011} , in some cases like, for instance, in floor cleaning robots, anthropomorphic characteristics could even be detrimental to robot's task accomplishment.
This generates the necessity to study other mechanisms that could help to project emotions, which could give people an idea about the robots' state, and engage the user in long term relations.

The amount of works studying non-anthropomorphic features in robotics (e.g.,~\cite{Saerbeck2010,Lakatos2014,Sharma2013,Novika2015}) remains still small in comparison to those that exploit anthropomorphic features. Moreover, these works do not give specific range of values for the characteristics used to expressed the emotions implemented by them. For example Suk and collaborators~\cite{NAM2014} in their study gives specific values for acceleration, curvature, and but their connection to specific emotions is not given. Rather, they gave a relationship between their features and values in terms of pleasure/arousal dimensions. This could lead to select features to convey certain emotions but it would be even better to know specific range of values for those features to convey certain emotions or to know the values that could be misinterpreted with negative emotions.

In order to get a better understanding of other features and values that could be used to convey specific emotions, this paper presents an experiment that was designed to identify specific values for some movement features that could be used to express the following emotions, selected among the ones suggested by Ekman as basic~\cite{Ekman2004}: happiness, anger, fear and sadness. The considered features are oscillation angle, linear and angular velocity, direction and orientation, identified as independent variables. The perceived emotions and their intensities were considered as dependent variables. It is to be observed that it was given the possibility to the subjects to provide their evaluation of emotional intensity for more than one emotion for each experience. The experiment took place in Politecnico di Milano during June and July of 2015, where students from diverse departments were asked to participate without any economical retribution. Krippendorff's alpha agreement~\cite{Krippendorff2007} ($\alpha$) was used to evaluate the agreement among the participants for each treatment. For each of the four emotions was generated a top 10 list based on alpha agreement and perceived intensity. The results suggest that fear is perceived when the robot is looking at them and moving far from them fast. Sadness is attributed to slow velocities with slow angular velocity and small oscillation angle. Anger is attributed to fast velocities, both angular and linear, small angle of oscillation and the robot facing the person when it is approaching them.

This paper is organized as follows. The next section introduces previous studies done in human emotion and robot emotions projection. Section~\ref{sec:system} introduces the robotic platform and the software used in the experiment. The experiment's design is explained in section~\ref{sec:experiment}. Finally sections~\ref{sec:study} and~\ref{sec:result} presents the study done and the obtained results.

>>>>

%TODO Here, even before what follows, the need for emotion expression should be justified, ad possibily supported by literature

Emotions and mental states are not just presented through facial expression, but also by body postures and other features~\cite{Gelder2008}. However,  many psychological studies have been mostly focused on understanding the role of human face in emotion projection~\cite{Ekman2004},~\cite{kleinsmith2012affective} and mental states. This trend has been followed by the robotics community, where anthropomorphic faces (e.g.,~\cite{Arras2012},~\cite{Breazeal2002}) and bodies (e.g.,~\cite{Canamero2010},~\cite{haering2011},~\cite{Destephe2013}) have been widely used to convey emotions.
Nevertheless, in many situations the presence of anthropomorphic elements would be out of place and not justified by the main robot's functionalities. Most of the current and future robotics platforms on the market will not require anthropomorphic faces~\cite{Breazeal2002} or limbs~\cite{Li2011}. In some cases, like, for instance, in floor cleaning robots, anthropomorphic characteristics could even be detrimental to robot's task accomplishment.
This generates the necessity to study other mechanisms that could help to project emotions, which could give people an idea about the robots' state, and engage the user in long term relations.

The amount of works studying non-anthropomorphic features in robotics (e.g.,~\cite{Saerbeck2010,Lakatos2014,Sharma2013,Novika2015}) remains still small in comparison to those that exploit anthropomorphic features. Moreover, these works do not prescribe any specific range of values for the characteristics to be used to express the  implemented emotionsb. For example, Suk and collaborators~\cite{NAM2014}, in their study, give specific values for acceleration, curvature, but their connection to specific emotions is not given. Rather, they give a relationship between their features and values in terms of valence and arousal. This could lead to select features to convey certain emotions, but it would be better to know the specific range of values for those features to convey the single emotions, or to know the values that could lead to misinterpret the emotional expression.

In order to get a better understanding of other features and values that could be used to convey specific emotions, this paper presents an experiment that was designed to identify specific values for some movement features that could be used to express the following emotions, selected among the ones suggested by Ekman as basic~\cite{Ekman2004}: happiness, anger, fear, and sadness. The considered features are: oscillation angle, linear and angular velocity, direction and orientation, identified as independent variables. The perceived emotions and their intensities were considered as dependent variables. It is to be observed that it was given the possibility to the subjects to provide their evaluation of emotional intensity for more than one emotion for each experience. The experiment took place in Politecnico di Milano during June and July of 2015, where students from diverse departments were asked to participate without any economical retribution. Krippendorff's alpha agreement~\cite{Krippendorff2007} ($\alpha$) was used to evaluate the agreement among the participants for each treatment. For each of the four emotions was generated a top 10 list based on alpha agreement and perceived intensity. The results suggest that fear is perceived when the robot is looking at the subjects while moving far from them fast. Sadness is associated to slow velocities with slow angular velocity and small oscillation angle. Anger is attributed to fast velocities, both angular and linear, small angle of oscillation and the robot facing the subjects while approaching them.

This paper is organized as follows. The next section introduces previous studies done in human emotion and robot emotions projection. Section~\ref{sec:system} introduces the robotic platform and the software used in the experiment. The experiment's design is explained in section~\ref{sec:experiment}. Finally sections~\ref{sec:study} and~\ref{sec:result} present the study done and the obtained results.

### 2016-10-08 JournalIJSR/Parts/Platform.tex
Changes in both articles.
Add files via upload

The system used in the experiment is composed by a non-anthropomorphic platform and software architecture that enrich robot's movements with emotion. The robotic platform was envisioned to be as simpler as possible to let the study of the desired characteristics.

@@

A holonomic platform was built to be used in the experiment. This type of platforms are characterized by the possibility to move in any direction without the necessity to have a specific orientation, i.e., they are free to move taking any desired orientation. Therefore, it was possible to imitate movements that are done by humans. For example, people move straight even if they turn their whole body a bit. The platform has a diameter of 25 cm and height of 25 cm. Figure~\ref{fig:ThirdDesign} shows the platform's blue prints and the real platform. Robot's frame of reference, in which all the velocities are going to be calculated, are depicted by the two black arrows. So, as it could be observed, to make the robot move forward it must be send a velocity in $y$ axis.

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{Images/DesignThird.png} 
	\caption{Design of the platform. a) Base platform, this layer is used to carry the batteries. The two black arrows represent robot's frame of reference. b) First layer, which includes the Arduino and the H-Bridges to control the motors. c) Second layer with the Odroid-U3 and the mechanical structure to support the upper part. d) Lateral view of the version.}
	\label{fig:ThirdDesign}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%platform_base
\subsection{Software}
To ensure robot's velocity it was implemented a PID controller for each motor. PID's set point is established by a controller that could receive two different types of commands. The first commands is robot's velocities ($<V_x,V_y,\omega>$), which are given in robot's frame of reference. The second command is a point ($<x, Y, \theta>$), which is given in the general frame of reference. This frame of reference is set every time the system is reset or boot. For example, if the robot finishes a trajectory and then it is reset, the new frame is going to be in the robot's current position.

Additional to this low level control, it was created a graphical interface~\ref{fig:experimental_interface} to reduce the possibility on introducing wrong values for a desired sequence. This interface loads the sequences from a .txt file and displays sequences' numbers on it. Every time that a new sequence should be presented to a participant, the sequence's number is selected in the interface, which will display sequence's values. Once the robot has been positioned to the correct position, the execution could be started by clicking on send button. Here two commands are send, one resetting the controller and the second the desire position. In case that the sequence's execution should be aborted, it should be clicked the button stop.

\begin{figure}
	\centering
	\includegraphics[width=0.60\textwidth]{./Images/ExperimentInterface.png} 
	\caption{Interface used in the experiment. Once a sequence is selected, the interface shows sequence's values. Also, the interface give information about the current position of the robot and its velocity.}
	\label{fig:experimental_interface}
\end{figure}

>>>>

The system used in the experiment is composed by a non-anthropomorphic platform and software architecture that enrich robot's movements with emotion. The robotic platform was envisioned to be as simple as possible to limit the influence of shape on the study of the desired characteristics.

@@

A holonomic platform was built to be used in the experiment. This type of platforms are characterized by the possibility to move in any direction without the necessity to have a specific orientation, i.e., they are free to move taking any desired orientation. Therefore, it was possible to imitate movements that are done by humans. For example, people do not have constaraints in movement, and can take any direction in any moment. The platform has a diameter of 25 cm and height of 25 cm. Figure~\ref{fig:ThirdDesign} shows the platform's blue prints and the real platform. Robot's frame of reference, in which all the velocities are going to be calculated, is depicted by the two black arrows. So, as it could be observed, to make the robot move forward a velocity along the $y$ axis is selected by the control system.

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{Images/DesignThird.png} 
	\caption{Design of the platform. a) Base platform, this layer is used to carry the batteries. The two black arrows represent robot's frame of reference. b) First layer, which includes Arduino and the H-Bridges to control the motors. c) Second layer with Odroid-U3 and the mechanical structure to support the upper part. d) Lateral view of the robot.}
	\label{fig:ThirdDesign}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%platform_base
\subsection{Software}
To guarantee that the correct robot's velocity for each motor could be achieved, a PID controller was implemented. PID's set point is established by a higher level controller that could receive two different types of commands. The first commands are robot's velocities ($<V_x,V_y,\omega>$), given in robot's reference frame. The second command is a set point ($<x, Y, \theta>$) to be reached, given in the world reference frame. This frame of reference is set every time the system is reset or boot. For example, if the robot finishes a trajectory and then it is reset, the new frame is going to be in the robot's current position.  %TODO From this description it seems that this second reference frame is again associated to the robot, in particular that it is a reference frame that is activated when the robot starts, and does not move with the robot. So it is a world reference frame reset each time the robot starts a new movement. It should have a name, to be found. If it was always associated with the robot it would have been called "deictic".

%TODO I'm sorry, but the following is an implementation detail that does not add anything to the scientific relevance of this paper, and this is not a paper about the interface.
%In addition to this low level control, a graphical interface, depicted in Figure~\ref{fig:experimental_interface}, was created to reduce the possibility of introducing wrong values for a desired sequence. This interface loads the sequences from a .txt file and displays sequences' numbers on it. Every time that a new sequence should be presented to a participant, the sequence's number is selected in the interface, which will display sequence's values. Once the robot has been positioned to the correct position, the execution could be started by clicking on send button. Here two commands are send, one resetting the controller and the second the desire position. In case that the sequence's execution should be aborted, it should be clicked the button stop.

%\begin{figure}
%	\centering
%	\includegraphics[width=0.45\textwidth]{./Images/ExperimentInterface.png} 
%	\caption{Interface used in the experiment. Once a sequence is selected, the interface shows sequence's values. Also, the interface give information about the current position of the robot and its velocity.}
%	\label{fig:experimental_interface}
%\end{figure}
